**The status of the microbial census: an update**

### 2015-12-01 Schloss_Census2_mBio_2015.Rmd
Fix typo

***New technologies to access novel biodiversity***
Assembly of metagenomic and single cell shotgun sequence data offers the hope of identifying large fragments of genomic data from as yet uncultured organisms. To test the ability of single cell technologies to expand our knowledge of microbial diversity beyond that of the 16S rRNA gene and pure cultures, we compared the overlap of OTUs found by the three methods (Figure venn_otu_by_method.pdf). Utilizing the 16S rRNA gene sequences extracted from the single-cell genomes available on the Integrated Microbial Genomes (IMG) system [@REF], we identified `r overlap_counts['n_sc', 'bact_counts']` bacterial and `r overlap_counts['n_sc', 'arch_counts']` archaeal sequences that met our criteria, which were assigned to `r overlap_counts["sc_all", "bact_counts"]` and `r overlap_counts["sc_all", "arch_counts"]`. Interestingly, only `r b_per_unique_sc` and `r a_per_unique_sc`% of the bacterial and archaeal OTUs, respectively, that the single-cell 16S rRNA gene sequences belonged to had not been observed by cultivation or PCR-based efforts. For both domains, the fractions of the single-cell 16S rRNA gene sequences that were recovered by cultivation and PCR were similar. Furthermore, among the bacteria `r b_per_shared`% of the single-cell OTUs were previously observed by both cultivation and PCR-based methods. Although the majority of single-cell genome projects have originated from a single study [@REF], `r b_expand_genome` and `r a_expand_genome` of the bacterial and archaeal OTUs, respectively, were from previously uncultured organisms. This represents an encouraging avenue to expanding our knowledge of bacterial diversity beyond the 16S rRNA gene.

>>>>

***New technologies to access novel biodiversity***
Assembly of metagenomic and single cell shotgun sequence data offers the hope of identifying large fragments of genomic data from as yet uncultured organisms. To test the ability of single cell technologies to expand our knowledge of microbial diversity beyond that of the 16S rRNA gene and pure cultures, we compared the overlap of OTUs found by the three methods (Figure venn_otu_by_method.pdf). Utilizing the 16S rRNA gene sequences extracted from the single-cell genomes available on the Integrated Microbial Genomes (IMG) system [@REF], we identified `r overlap_counts['n_sc', 'bact_counts']` bacterial and `r overlap_counts['n_sc', 'arch_counts']` archaeal sequences that met our criteria, which were assigned to `r overlap_counts["sc_all", "bact_counts"]` and `r overlap_counts["sc_all", "arch_counts"]` bacterial and archaeal OTUs, respectively. Interestingly, only `r b_per_unique_sc` and `r a_per_unique_sc`% of the bacterial and archaeal OTUs, respectively, that the single-cell 16S rRNA gene sequences belonged to had not been observed by cultivation or PCR-based efforts. For both domains, the fractions of the single-cell 16S rRNA gene sequences that were recovered by cultivation and PCR were similar. Furthermore, among the bacteria `r b_per_shared`% of the single-cell OTUs were previously observed by both cultivation and PCR-based methods. Although the majority of single-cell genome projects have originated from a single study [@REF], `r b_expand_genome` and `r a_expand_genome` of the bacterial and archaeal OTUs, respectively, were from previously uncultured organisms. This represents an encouraging avenue to expanding our knowledge of bacterial diversity beyond the 16S rRNA gene.
